\normalfont \normalsize \textsc{University of Stuttgart} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Hauptseminar:\\The Logjam Attack \\ \horrule{2pt} \\[0.5cm]

### 2017-06-26 Ausarbeitung/paper.tex
post deadline corrections no 1
Z[alpha] -> Z[gamma],
Sieving: got the smoothnes criteria wrong

Next, let $\gamma\in\mathbb{C}$ be the root of $f$, define $K = \mathbb{Q}(\gamma) = \mathbb{Q}\cup\{\gamma\}$ and $O_K$ the ring of integers in $K$. Since $\mathrm{gcd}(q,\Delta_f) = 1$, $\hat{q}:=(q,\gamma-m)$ is a first-degree prime factor of $q\in O_K$. It follows that $O_K/\hat{q}\cong\mathrm{GF}(q)$ and we can define a homomorphism $\phi:\mathbb{Z}[\alpha]\rightarrow\mathbb{Z}/q\mathbb{Z}$, providing us the representation we aimed for. We denote a prime ideal $s\in O_K$ as \textit{good} if $s$ does not divide the index $[O_K:\mathbb{Z}[\gamma]]$, otherwise we denote it as \textit{bad}.

@@

\subsubsection{Sieving}
In this step we try to find linear equations that are informative in the sense that they are related to the the logarithms in $\mathcal{B}$. For that, sieve through integer pairs $(c,d)$ that are co-prime for which $c+dm$ and $c+d\gamma$ are $S$-smooth where $S = \prod_{s\in\mathcal{B}_\mathbb{Q}}$. For this smoothness criteria, we can formulate equations
\begin{eqnarray}
c+dm = \prod_{s\in\mathcal{B}_\mathbb{Q}}s^{w_s(c,d)}
\end{eqnarray}
and
\begin{eqnarray}
|N(c+d\gamma)| = \prod_{s\in\mathcal{B}_\mathbb{Q}}s^{v_s(c,d)}
\text{ ,}
\end{eqnarray}
where $N(c+d\gamma) = (-d)^kf(-\frac{c}{d})$ (see original paper \citep{gordon1993discrete} for explanation), for some $w_s,v_s\in\mathbb{Z}^+$.

>>>>

Next, let $\gamma\in\mathbb{C}$ be the root of $f$, define $K = \mathbb{Q}(\gamma) = \mathbb{Q}\cup\{\gamma\}$ and $O_K$ the ring of integers in $K$. Since $\mathrm{gcd}(q,\Delta_f) = 1$, $\hat{q}:=(q,\gamma-m)$ is a first-degree prime factor of $q\in O_K$. It follows that $O_K/\hat{q}\cong\mathrm{GF}(q)$ and we can define a homomorphism $\phi:\mathbb{Z}[\gamma]\rightarrow\mathbb{Z}/q\mathbb{Z}$, providing us the representation we aimed for. We denote a prime ideal $s\in O_K$ as \textit{good} if $s$ does not divide the index $[O_K:\mathbb{Z}[\gamma]]$, otherwise we denote it as \textit{bad}.

@@

\subsubsection{Sieving}
In this step we try to find linear equations that are informative in the sense that they are related to the the logarithms in $\mathcal{B}$. For that, sieve through integer pairs $(c,d)$ that are co-prime for which $c+dm$ and $c+d\gamma$ are $p$-smooth for at least one $p\in\mathcal{B}_\mathbb{Q}$. For this smoothness criteria, we can formulate equations
\begin{eqnarray}
c+dm = \prod_{s\in\mathcal{B}_\mathbb{Q}}s^{w_s(c,d)}
\end{eqnarray}
and
\begin{eqnarray}
|N(c+d\gamma)| = \prod_{s\in\mathcal{B}_\mathbb{Q}}s^{v_s(c,d)}
\text{ ,}
\end{eqnarray}
where $N(c+d\gamma) = (-d)^kf(-\frac{c}{d})$ (see original paper \citep{gordon1993discrete} for explanation), for some $w_s,v_s\in\mathbb{Z}^+$.
